---
title: "UNIT 05 HW"
author: "Jeremy Lubich"
date: "October 8, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1 - Data Munging - yob2016.txt

### 1.a Import File

```{r 1.a}

#setwd("C:/Users/LubichJD/OneDrive - Unisys/SMU/DDS/MyGitHubFiles/MSDS-Jeremy-Lubich/HW_UNIT_05")

df <- read.delim("yob2016.txt", sep = ";", header= FALSE, col.names = c("Name", "Gender", "Count"))

```

### 1.b Display Summary and Structure

```{r 1.b}

summary(df)
str(df)

```

### 1.c Find and display the record with yyy at the end

```{r 1.c}

subset(df, grepl("yyy", df$Name))

```

### 1.d Remove the bad record and save as y2016

```{r 1.d}

y2016 <- df[-grepl("yyy", df$Name), ]

````

## Question 2 - Data Merging 

### 2.a Import File yob2015.txt as y2015

```{r 2.a}

y2015 <- read.delim("yob2015.txt", sep = ",", header= FALSE, col.names = c("Name", "Gender", "Count"))

```

### 2.b Display last 10 rows and comment on what you see

```{r 2.b}

tail(y2015, 10)
print("Interesting, the last 10 rows are all boys")

````

### 2.c Merge t2015 & y2016 inner join on Name, assign to final

```{r 2.c}

final <- merge(
    y2015, 
    y2016, 
    by.x = "Name", 
    by.y = "Name"
)

```

## Question 3 - Data Summary

### 3.a Create "Total" column and display the total 

```{r 3.a}

final$Total <- final$Count.x + final$Count.y

```

### 3.b Sort by Total, List the top 10 most popular names

```{r 3.b}

final <- final[order(-final$Total), ]
head(final, 10)

```

### 3.c Omit Boys names and give top 10 girls names

```{r 3.c}

head(final[final$Gender.x == "F", ], 10)

```

### 3.d Write the top 10 girls names and Totals to a CSV, leaving other columns out

```{r 3.d}

top.10.girls <- head(final[final$Gender.x == "F", c("Name", "Total")], 10)
write.csv(top.10.girls, "Top10GirlNames.csv", row.names = FALSE)

```

## Question 4 - Upload to Github

### Codebook is called: *README*

### My Github Repo URL:
https://github.com/jlubich/MSDS-Jeremy-Lubich

### This Assignment URL:
https://github.com/jlubich/MSDS-Jeremy-Lubich/tree/master/HW_UNIT_05

# Session Info

```{r session_info}

sessionInfo()
```

